Rotations and Insecticide Resistance initial plots

### 2017-11-22 inst/documents/rotations1.Rmd
rename rotation_ vars to rot_, add sentence to UI about rotate when resistant at interval 0

#expo_hi=c(1,0.1)
dfr <- run_rot(n=2, rotation_interval=100, expo_hi=c(1,0.1))

@@

# TODO remove hardcode fitnesses from here
dfr <- run_rot(rotation_interval=50, max_gen = 300, hardcode_fitness = TRUE, same_insecticides =TRUE, migration=0.01)

@@

dfr <- run_rot(rotation_interval=50, max_gen = 300, hardcode_fitness = TRUE, same_insecticides =TRUE, migration=0.001)

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.show='hold', fig.align='left', fig.cap="cost 0.1 effectiveness 1"}
dfr <- run_rot(n=3, rotation_interval=50, eff=1, cost=0.1)
```

@@

dfr <- run_rot(rotation_interval=0, max_gen = 300, hardcode_fitness = TRUE, same_insecticides =TRUE, expo_hi=0.5, migration=0.01)

@@

run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.1 , rotation_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0.01 , cost = 0.1 )

@@

run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.1 , rotation_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0.01 , cost = 0 )

>>>>

#expo_hi=c(1,0.1)
dfr <- run_rot(n=2, rot_interval=100, expo_hi=c(1,0.1))

@@

# TODO remove hardcode fitnesses from here
dfr <- run_rot(rot_interval=50, max_gen = 300, hardcode_fitness = TRUE, same_insecticides =TRUE, migration=0.01)

@@

dfr <- run_rot(rot_interval=50, max_gen = 300, hardcode_fitness = TRUE, same_insecticides =TRUE, migration=0.001)

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.show='hold', fig.align='left', fig.cap="cost 0.1 effectiveness 1"}
dfr <- run_rot(n=3, rot_interval=50, eff=1, cost=0.1)
```

@@

dfr <- run_rot(rot_interval=0, max_gen = 300, hardcode_fitness = TRUE, same_insecticides =TRUE, expo_hi=0.5, migration=0.01)

@@

run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.1 , rot_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0.01 , cost = 0.1 )

@@

run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.1 , rot_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0.01 , cost = 0 )

### 2017-11-22 inst/documents/rotations_notes.Rmd
rename rotation_ vars to rot_, add sentence to UI about rotate when resistant at interval 0

implemented set_expsoure_rot() now working
dfr <- run_rot(rotation_interval=50, expo_hi=0.9)
dfr <- run_rot(rotation_interval=50, expo_hi=0.2)
# diff frequency curves for r1 & r2
dfr <- run_rot(n=2, rotation_interval=50, expo_hi=c(1,0.1))

@@

dfr <- run_rot(n=2, rotation_interval=50, eff=c(1,0.1))

@@

run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.1 , rotation_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration_rate_intervention = 0.01 , cost = 0.1 )

@@

run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.1 , rotation_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration_rate_intervention = 0.01 , cost = 0 )

@@

n_insecticides    | 3,4,5
max_gen   | 
rotation_interval | 5 - 50 (integer)
male_expo_prop    | 0 - 1
coverage          | 0.1 - 0.9
migration         |  
cost              | 0 - 0.05

@@

#high cost, no migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rotation_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0.1 , logy = FALSE )
#no cost, no migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rotation_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0 , logy = FALSE )
#no cost and rotate when resistant, no migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rotation_interval = 0 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0 , logy = FALSE )
#no cost, some migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rotation_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0.05 , cost = 0 , logy = FALSE )

@@

@@

~ take the insecticide switching out into its own function(s)

>>>>

implemented set_expsoure_rot() now working
dfr <- run_rot(rot_interval=50, expo_hi=0.9)
dfr <- run_rot(rot_interval=50, expo_hi=0.2)
# diff frequency curves for r1 & r2
dfr <- run_rot(n=2, rot_interval=50, expo_hi=c(1,0.1))

@@

dfr <- run_rot(n=2, rot_interval=50, eff=c(1,0.1))

@@

run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.1 , rot_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration_rate_intervention = 0.01 , cost = 0.1 )

@@

run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.1 , rot_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration_rate_intervention = 0.01 , cost = 0 )

@@

n_insecticides    | 3,4,5
max_gen   | 
rot_interval | 5 - 50 (integer)
male_expo_prop    | 0 - 1
coverage          | 0.1 - 0.9
migration         |  
cost              | 0 - 0.05

@@

#high cost, no migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rot_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0.1 , logy = FALSE )
#no cost, no migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rot_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0 , logy = FALSE )
#no cost and rotate when resistant, no migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rot_interval = 0 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0 , logy = FALSE )
#no cost, some migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rot_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0.05 , cost = 0 , logy = FALSE )

@@

*22/11/17*

# check with Ian
~ insecticide switch criterion is female only

@@

~ take the insecticide switching out into its own function(s)
insecticide_check()
insecticide_switch()
